%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {University of Illinois Chicago} % Institution
    {M.S. in Computer Science} % Degree
    {Chicago, USA} % Location
    {August 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Working on a research project in the field of medical imaging to determine the existence of correlation between heart disease and erythrocyte flow in the eye's blood vessels using computer vision and machine learning.}
        \item {Developing an AI based company in the field of ecommerce as part of a course. Involved in developing the product map, market strategy and developing recommendation systems of various types.}
        \item {Developed an Aspect based Sentiment Analysis system that beats state of the art accuracy.}
        \item {Created an application that learns human behavior in an environment. Applied it to learn driving from F1 2017 game.}
        \item {Worked with the company, Explorer.ai to create deep learning models in the context of 3D mapping for self driving cars. Performed real-time traffic sign detection.}
        \item {Gave a 2+ hour talk on computer vision and classification and detection problem. Experimented across various NLP problems and implementing recent research papers.}
        \item {Developed solutions for Kaggle problems like Otto Product Classification and Young People Empathy Prediction.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {National Institute of Technology, Karnataka} % Institution
    {B.Tech. in Electronics and Communication Engineering} % Degree
    {Karnataka, India} % Location
    {July 2011 - May 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Developed a real-time low-cost portable OCR system aimed at allowing visually challenged people to read printed text.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
