%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Relevant Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Science Intern} % Job title
    {Datacubes Inc.} % Organization
    {Chicago, USA} % Location
    {May 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Re-engineering the entire OCR pipeline to handle insurance related documents using image processing, deep learning and other machine learning techniques to beat their current system and other SOTA OCR platforms.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer - Innovation ( Data Science and AI)} % Job title
    {Emirates Innovation Lab, Emirates Group} % Organization
    {Dubai, U.A.E} % Location
    {July 2015 - July 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Initiated and co-developed the 'CogniFace' platform - a face recognition platform based on CMU Open Face. Also developed use cases built around this platform like a system similar to Amazon Go, presence monitoring, reminder prompting etc. }
        \item {Worked on 'Predictive Capping' project predicting agent fraud using machine learning techniques. Obtained an accuracy of upto 91\% with booking data saving the company 6 million dollars every year.}
        \item {Led the projecton R\&D for a vacation recommender architecture using machine learning and graph networks.}
        \item {iOS Team Lead and Developer for 'Skywards'. Led a team of 5 and developed a production level non-trivial iOS app on Swift.}
        \item {Full stack developer on 'Skywards Engagement Platform'. Developed a social media system through Neo4J, a graph
database (using CYPHER Query Language). Involved in writing the REST services on Spring Boot ( Java Spring Framework).}
        \item {Developed hybrid applications for mobile and Web using Cordova and Angular JS.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
